Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative

### 2021-09-11 paper/dcpo_gender_roles.Rmd

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere"
thanks: "Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Byung-Deuk Woo
  affiliation: University of Iowa
- name: Lindsey Allemang
  affiliation: University of Iowa
- name: Frederick Solt
  affiliation: University of Iowa
anonymous: false
abstract: "Societal attitudes toward gender roles in the workplace and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories. Drawing on recent advances in latent variable modeling of public opinion and a comprehensive collection of survey data, we present the Public Gender Egalitarianism dataset to address this need: comparable estimates of the public's attitudes on gender equality in the public sphere across more than one hundred countries over time. These PGE scores are strongly correlated with responses to individual survey items and with women's rates of participation in the labor force and corporate boards. We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere. [148/150 words]"
keywords: "gender roles, gender inequality, public opinion, political culture, measurement"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture, norms, ideology, or public opinion---constitute one of the primary explanations for women's exclusion from the traditionally masculine public sphere of the workforce, political power, and policy influence [see, e.g., @Gray2006, 299-302; @Yates2017, 103-104; @Paxton2021, 113-114].
Yet even a half century after @RuleKrauss1974 [, 1719] called for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
Cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained persistently a topic for future research [@Paxton2010, 47].

@@

Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do."
Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years.
That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic.

@@

We used the `DCPO` package for R [@Solt2020a] to estimate this model on the public gender egalitarianism source data described above.
The dispersion parameters of the survey items indicate that all of them load well on the latent variable (see online Appendix A).^[
To provide further confirmation of the unidimensionality of public gender egalitarianism, we divided the source data described above to estimate separate indices of gender egalitarianism (a) in politics and (b) in the workplace.  The two resulting indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.]
The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.
Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries and territories in the dataset.

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms2.tex
title: "Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere"
thanks: "Corresponding author: [frederick-solt@uiowa.edu](mailto:frederick-solt@uiowa.edu).  Current version: `r format(Sys.time(), '%B %d, %Y')`."
author:
- name: Byung-Deuk Woo
  affiliation: University of Iowa
- name: Lindsey Allemang
  affiliation: University of Iowa
- name: Frederick Solt
  affiliation: University of Iowa
anonymous: true
abstract: "Societal attitudes toward gender roles in the workplace and politics play a central part in theorizing on the difficulty women face in achieving political equality, but shortcomings in the available data have prevented direct examination of many implications of these theories. Drawing on recent advances in latent variable modeling of public opinion and a comprehensive collection of survey data, we present the Public Gender Egalitarianism dataset to address this need: comparable estimates of the public's attitudes on gender equality in the public sphere across more than one hundred countries over time. These PGE scores are strongly correlated with responses to individual survey items and with women's rates of participation in the labor force and corporate boards. We expect that the PGE data will become an invaluable source for broadly cross-national and longitudinal research on the causes and consequences of collective attitudes toward gender equality in the public sphere. [148/150 words]"
keywords: "gender roles, gender inequality, public opinion, political culture, measurement"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
spacing: double
bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture, norms, ideology, or public opinion---constitute one of the primary explanations for women's exclusion from the traditionally masculine public sphere of the workforce, political power, and policy influence [see, e.g., @Paxton2021, 113-114].
Yet even a half century after @RuleKrauss1974 [, 1719] called for more and better data on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in office [see, e.g., @Burns2001, 340-341; @Claveria2014; @Barnes2018].
Cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained persistently a topic for future research [@Paxton2010, 47].

@@

<!-- Consider the most frequently asked item in the data we collected, which asks respondents whether they strongly agree, agree, disagree, or strongly disagree with the statement "On the whole, men make better political leaders than women do." -->
<!-- Employed by the Americas Barometer, the Arab Barometer, the Eurobarometer, the Latinobarómetro, the Pew Research Center, and the World Values Survey, this question was asked in a total of `r polileader4_cy` different country-years. -->
<!-- That this constitutes only `r {polileader4_cy*100/(spanned_cy %>% str_replace(",", "") %>% as.numeric())} %>% round()`% of the country-years spanned by our data---and remember, this is the _most common_ survey item---again underscores just how sparse and incomparable the available public opinion data is on this topic. -->

@@

We used the `DCPO` package for R [@Solt2020a] to estimate this model on the public gender egalitarianism source data described above.
The dispersion parameters of the survey items indicate that all of them load well on the latent variable (see online Appendix A).
The result is estimates, in all `r res_cy` country-years spanned by the source data, of mean public gender egalitarianism, what we call PGE scores.^[
To provide further confirmation of the unidimensionality of public gender egalitarianism, we estimated two separate indices of gender egalitarianism in politics and in the workplace.  These indices correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years; see online Appendix C.]
Figure&nbsp;\ref{cs_mry} displays the most recent available PGE score for each of the `r res_c` countries and territories in the dataset.

### 2021-09-11 paper/pge_appendix.Rmd

dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public)

@@

items_summary <- dcpo_input_raw_public1 %>%
    dplyr::select(country, year, item, survey) %>%
    distinct() %>%
    separate(survey, c("surv1", "surv2", "surv3"), sep=", ", fill = "left") %>%
    pivot_longer(cols = starts_with("surv"), values_to = "survey") %>%
    filter(!is.na(survey)) %>% 
    group_by(item, survey) %>% 
    summarize(n_cy = n()) %>% 
    arrange(item, -n_cy) %>% 
    group_by(item) %>% 
    mutate(total_cy = sum(n_cy),
           all_surveys = paste0(survey, collapse = ", ")) %>% 
    slice(1) %>% 
    ungroup() %>% 
    left_join(pge_items %>% select(item, survey, question_text),
              by = c("item", "survey")) %>% 
    left_join(alpha_results, by = "item") %>% 
    left_join(beta_results, by = "item") %>% 
    arrange(-total_cy) %>% 
    select(-survey, -n_cy)
```

@@

```{r pge_items_table4}    
pge_items_table(24:31)
```

```{r pge_items_table5}    
pge_items_table(32:42)
```

\pagebreak
```{r pge_items_table6}    
pge_items_table(43:50)
```
\vspace{-.95in}
Notes: Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found within the typical cross-national survey dataset.  Lower values of dispersion ($\alpha$) indicate questions that better identify publics with more public gender egalitarianism from those with less.  Items have one difficulty score ($\beta$) for each cutpoint; that is, one less than the number of response categories.  Survey dataset codes correspond to those used in the `DCPOtools` R package; they appear in decreasing order of country-years contributed.

\pagebreak
# Appendix B: Excluded Survey Items
To estimate the Public Gender Egalitarianism scores, we collected survey data on questions asking respondents' views of gender equality in the traditionally masculine public sphere of education, paid work, and politics.
These included questions are nearly always explicit in comparing men and women (but see, for example, `unequalpol4`, which asked responses to the statement "Women do not have the necessary qualities and skills to fill positions of responsibility in politics") and nearly always explicitly invoke education, paid work, or politics, though they may also be broader (see, for example, `equalright2`, which asked "On a different subject, do you think women should have equal rights with men, or shouldn’t they?").

We carefully distinguished these questions from three other categories of questions on gender equality.
First, the PGE source data do not include the small set of questions focusing on gender equality in the traditionally feminine private sphere of housework and childcare, such as "Men should take as much responsibility as women for the home and children," asked (with differing response categories) in the European Values Survey and the European Social Survey.
Second, as noted in the text, we also excluded questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not, asked in the World Values Survey and many others.
Given that attitudes that women should prioritize housework and childcare over education, paid employment, and politics---or convictions that there will be negative consequences if they do not---can be expected to lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, this is clearly a very closely related set of items to those we sought, and there are many of them.^[
It is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys; one laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
The third and final category of excluded survey items includes respondents' views on various forms of women's domination by men, from whether wives should adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
In each case, as the included questions are not _directly_ relevant to gender egalitarianism in the public sphere, we concluded that to ensure that the PGE scores tap only a single dimension of attitudes, we would exclude these others.
Usefully, this decision also allows, when the available survey data permits, future research to take up the estimation of dynamic comparative public opinion of those concepts separately and their relationships to public gender egalitarianism.

@@

To provide further confirmation of the unidimensionality of public gender egalitarianism, we used the survey items listed in Appendix A to estimate separate indices of gender egalitarianism in politics, in the workplace, and in education.  As shown in Figure \ref{pge_pwe_corr_plot}, these three indices all correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years.

@@

dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public) %>% 
  left_join(public_items, by = "item")
dcpo_input_raw_political1 <- dcpo_input_raw_public1 %>% 
  filter(political==1)
dcpo_input_raw_workplace1 <- dcpo_input_raw_public1 %>% 
  filter(workplace==1)
dcpo_input_raw_education1 <- dcpo_input_raw_public1 %>% 
  filter(education==1)

@@

dcpo_input_education <- DCPOtools::format_dcpo(dcpo_input_raw_education1,
                                            scale_q = "education4",
                                            scale_cp = 2)
save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))
```

@@

```{r dcpo_education, eval=FALSE}
iter <- 5000

dcpo_output_education <- dcpo(dcpo_input_education,
                              iter = iter,
                              chains = 4,
                              thin = iter/500, # this yields 250 draws per chain, 1000 draws total
                              pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))
```

```{r political}
load(here::here("data", "political_polileader4_2_4k.rda"))

@@

```{r education}
load(here::here("data", "education_education4_2_5k.rda"))

dcpo_input_education <- dcpo_input

dcpo_output_education <- dcpo_output

save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))

save(dcpo_output_education, file = here::here("data", "dcpo_output_education.rda"))
```

@@

```{r theta_res_education}
load(here::here("data", "dcpo_input_education.rda"))
load(here::here("data", "dcpo_output_education.rda"))

dat <- dcpo_input_education$data

theta_res_education <- rstan::extract(dcpo_output_education, pars = "theta") %>%
        dplyr::first() %>%
        purrr::array_branch(1) %>%
        purrr::map(function(x) {
          tibble::as_tibble(x) %>%
          dplyr::mutate(tt = dplyr::row_number()) %>%
            dplyr::left_join(tcodes, by = "tt") %>%
            tidyr::pivot_longer(cols = starts_with("V"),
                                names_to = "kk",
                                values_to = "pge_mean") %>%
            dplyr::mutate(year = if_else(tt == 1,
                                         as.integer(year),
                                         as.integer(min(year, na.rm = TRUE) + tt - 1)),
                          kk = stringr::str_replace(kk, "V", "") %>% as.numeric()) %>%
            dplyr::left_join(kcodes, by = "kk") %>%
            dplyr::left_join(ktcodes, by = "country") %>%
            dplyr::filter(year >= first_yr & year <= last_yr) %>%
            dplyr::arrange(kk, tt) %>%
            dplyr::select(country, year, pge_mean) %>% 
            dplyr::rename(education_mean = pge_mean)
        })
```

@@

pge_pw <- map(1:1000, function(x) {
  pge[[x]] %>% 
    left_join(theta_res_political[[x]], by = c("country", "year")) %>% 
    left_join(theta_res_workplace[[x]], by = c("country", "year")) %>% 
    left_join(theta_res_education[[x]], by = c("country", "year"))
})

@@

pge_education_cor <- map(pge_pw, function(x) {
  with(x, cor(pge_mean, education_mean, use = "pairwise.complete.obs"))
  }) %>% 
  unlist() %>% 
  mean() %>% 
  round(2)

@@

political_education_cor <- map(pge_pw, function(x) {
  with(x, cor(political_mean, education_mean, use = "pairwise.complete.obs"))
  }) %>% 
  unlist() %>% 
  mean() %>% 
  round(2)

workplace_education_cor <- map(pge_pw, function(x) {
  with(x, cor(workplace_mean, education_mean, use = "pairwise.complete.obs"))
  }) %>% 
  unlist() %>% 
  mean() %>% 
  round(2)

pge_pwe_corr_matrix <- matrix(c(1, pge_political_cor, pge_workplace_cor, pge_education_cor,
                                pge_political_cor, 1, political_workplace_cor, political_education_cor,
                                pge_workplace_cor, political_workplace_cor, 1, workplace_education_cor,
                                pge_education_cor, political_education_cor, workplace_education_cor, 1), ncol = 4)
colnames(pge_pwe_corr_matrix) <- c("Public\nGender\nEgalitarianism", "Political\nGender\nEgalitarianism", "Workplace\nGender\nEgalitarianism", "Education\nGender\nEgalitarianism")
```

```{r pge_pwe_corr_plot, fig.width=7, fig.cap = "Pairwise Correlations Among PGE Index and Separate Political, Workplace, and Education Egalitarianism Indices  \\label{pge_pwe_corr_plot}"}
corrplot::corrplot.mixed(pge_pwe_corr_matrix, tl.col = "black", tl.cex = .8, upper = "ellipse")
```

>>>>

dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public) %>% 
  left_join(public_items, by = "item")
dcpo_input_raw_poliwork1 <- dcpo_input_raw_public1 %>% 
  filter(political==1|workplace==1)

@@

items_summary <- dcpo_input_raw_poliwork1 %>%
    dplyr::select(country, year, item, survey) %>%
    distinct() %>%
    separate(survey, c("surv1", "surv2", "surv3"), sep=", ", fill = "left") %>%
    pivot_longer(cols = starts_with("surv"), values_to = "survey") %>%
    filter(!is.na(survey)) %>% 
    group_by(item, survey) %>% 
    summarize(n_cy = n()) %>% 
    arrange(item, -n_cy) %>% 
    group_by(item) %>% 
    mutate(total_cy = sum(n_cy),
           all_surveys = paste0(survey, collapse = ", ")) %>% 
    slice(1) %>% 
    ungroup() %>% 
    left_join(pge_items %>% select(item, survey, question_text),
              by = c("item", "survey")) %>% 
    left_join(alpha_results, by = "item") %>% 
    left_join(beta_results, by = "item") %>% 
    arrange(-total_cy) %>% 
    select(-survey, -n_cy)
```

@@

```{r pge_items_table4}    
pge_items_table(24:30)
```

```{r pge_items_table5}    
pge_items_table(31:41)
```

\pagebreak
```{r pge_items_table6}    
pge_items_table(42:50)
```
\vspace{-.95in}
Notes: Question text may vary slightly across survey datasets, but not, roughly speaking, by more than the translation differences across languages found within the typical cross-national survey dataset.  Lower values of dispersion ($\alpha$) indicate questions that better identify publics with more public gender egalitarianism from those with less.  Items have one difficulty score ($\beta$) for each cutpoint; that is, one less than the number of response categories.  Survey dataset codes correspond to those used in the `DCPOtools` R package; they appear in decreasing order of country-years contributed.

\pagebreak
# Appendix B: Excluded Survey Items
To estimate the Public Gender Egalitarianism scores, we collected survey data on questions asking respondents' views of gender equality in the traditionally masculine public sphere of paid work and politics.
These included questions are nearly always explicit in comparing men and women (but see, for example, `unequalpol4`, which asked responses to the statement "Women do not have the necessary qualities and skills to fill positions of responsibility in politics") and nearly always explicitly invoke either paid work or politics, though they may also be broader (see, for example, `equalright2`, which asked "On a different subject, do you think women should have equal rights with men, or shouldn’t they?").

We carefully distinguished these questions from three other categories of questions on gender equality.
First, the PGE source data do not include the small set of questions focusing on gender equality in the traditionally feminine private sphere of housework and childcare, such as "Men should take as much responsibility as women for the home and children," asked (with differing response categories) in the European Values Survey and the European Social Survey.
Second, as noted in the text, we also excluded questions asking respondents how women should balance opportunities in the public sphere with their traditional duties in the private sphere, such as whether mothers in the workforce can have similarly warm relationships with their children as mothers who are not, asked in the World Values Survey and many others.
Given that attitudes that women should prioritize housework and childcare over paid employment and politics---or convictions that there will be negative consequences if they do not---can be expected to lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, this is clearly a very closely related set of items to those we sought, and there are many of them.^[
It is telling, though not surprising, that the complementary set of questions, on how _men_ should balance responsibilities in the private sphere with their traditional roles in the public sphere, is only rarely included in surveys; one laudable example of this mostly unasked sort of question, apparently first included in Australia's 1989 National Social Science Survey and slowly becoming more common, is the item querying respondents the extent to which they agree with the statement, "Family life often suffers when men concentrate too much on their work."]
The third and final category of excluded survey items includes respondents' views on various forms of women's domination by men, from whether wives should always adopt their husbands' surnames through the recognition that various forms of sexual harassment are not "flattering" to the justifiability of intimate partner violence committed by husbands.
In each case, as the included questions are not _directly_ relevant to gender egalitarianism in the public sphere, we concluded that to ensure that the PGE scores tap only a single dimension of attitudes, we would exclude these others (see also Appendix C).
Usefully, this decision also allows, when the available survey data permits, future research to take up the estimation of dynamic comparative public opinion of those concepts separately and their relationships to public gender egalitarianism.

@@

To provide further confirmation of the unidimensionality of public gender egalitarianism, we used the survey items listed in Appendix A to estimate separate indices of gender egalitarianism in politics and in the workplace.  As shown in Figure \ref{pge_pwe_corr_plot}, these two indices both correlate very highly with the PGE scores and with each other, reinforcing the conclusion that public gender egalitarianism exists as a single dimension across countries and years.

@@

dcpo_input_raw_public1 <- process_dcpo_input_raw(dcpo_input_raw_public) %>% 
  left_join(public_items, by = "item")
dcpo_input_raw_political1 <- dcpo_input_raw_public1 %>% 
  filter(political==1)
dcpo_input_raw_workplace1 <- dcpo_input_raw_public1 %>% 
  filter(workplace==1)

@@

```

@@

```{r political, eval=FALSE}
load(here::here("data", "political_polileader4_2_4k.rda"))

@@

@@

@@

pge_pw <- map(1:1000, function(x) {
  pge[[x]] %>% 
    left_join(theta_res_political[[x]], by = c("country", "year")) %>% 
    left_join(theta_res_workplace[[x]], by = c("country", "year"))
})

@@

@@

pge_pwe_corr_matrix <- matrix(c(1, pge_political_cor, pge_workplace_cor,
                                pge_political_cor, 1, political_workplace_cor,
                                pge_workplace_cor, political_workplace_cor, 1),
                              ncol = 3)
colnames(pge_pwe_corr_matrix) <- c("Public\nGender\nEgalitarianism", "Political\nGender\nEgalitarianism", "Workplace\nGender\nEgalitarianism")
```

```{r pge_pwe_corr_plot, fig.width=7, fig.cap = "Pairwise Correlations Among PGE Index and Separate Political and Workplace Egalitarianism Indices  \\label{pge_pwe_corr_plot}"}
corrplot::corrplot.mixed(pge_pwe_corr_matrix, tl.col = "black", tl.cex = .8, upper = "ellipse")
```
